---
title: "Skills Problem Set VI"
author: "Sabrina Li"
date: "28/05/2021"
output: 
  pdf_document:
    number_sections: yes
  html_document:
    df_print: paged
urlcolor: blue
---
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyverse)
library(lubridate)
library(moments)


```

<!-- .Rmd files use  markdown, a text mark up language, to provide formating.--> 
<!--Text include within these strange arrows are comments and will not show up when you knit-->

# Front matter
This submission is my work alone and complies with the 30535 integrity policy.

Add your initials to indicate your agreement: **__**

Add your collaborators: **__**

Late coins used this pset: 0. Late coins left: X. 
<!--You may use up to two for a given assignment.)-->

# Problems

## Functions


### 1

```{r}
paste_str = function(vec){
  
  len = length(vec)
  return(paste(vec[-len], collapse = ', ') %>% paste(., vec[len], sep = ' and ')
  )
  
}

# test 
paste_str(c('a', 'b', 'c', 'd'))
```


### 2

```{r}
get_age =  function(dt){
  
  df = difftime(today(), dt, units = 'days') %>% as.numeric() / 365
  return(floor(df))
} 

# test
get_age(ymd('20110101'))
```

### 3


```{r}
get_variance = function(vec){
  
  return(sd(vec, na.rm = T) ** 2)
}


get_skew = function(vec){
  
  return(skewness(vec, na.rm = T))
}


diamonds %>% summarize_if(is.numeric,
                          list(avg = mean, 
                               var = get_variance, 
                               skewness = get_skew)) %>%
  matrix(ncol = 3,byrow = F) %>% as.data.frame() -> stats_diam


rownames(stats_diam) = diamonds %>% summarize_if(is.numeric, mean) %>% colnames()
colnames(stats_diam) = c('mean', 'variance', 'skewness')
stats_diam
```


### 4
```{r}
check_prefix <- function(string, prefix){
  str_sub(string, 1, nchar(prefix)) == prefix
}

check_prefix('hello', 'he')
remove_last_elements <- function(x){
  if (length(x) <= 1)return(NULL)
  return(x[-length(x)])
}
remove_last_elements(c(1,2,4))
```


### 5
```{r}
func_greeting = function(){
  
  h = now() %>% hour()
  if( h > 6 & h <= 12 ) print('good morning')
  if( h > 12 & h <= 18 ){
    print('good afternoon')
  } else{
    print('good evening')
  }
  
  
}

func_greeting()
```


## Loops


### 1

```{r}
for (i in colnames(mtcars)) {
  print(i)
  print(mean(mtcars[,i], na.rm = T))
}

for (i in colnames(mpg)) {
  print(i)
  print(length(unique(mpg[,i]) %>% unlist()))
}

ls = c(1,3,10,30, 100)
matrix(NA, nrow = 10, ncol = length(ls) ) ->res
colnames(res) = ls

for(i in 1: length(ls)){
  for (j in 1:10) {
    res[j, i] = rpois(1, lambda = ls[i])
  }
}
res
```


### 2

```{}
res = NULL

for (f in files) {
  
  tmp = read.csv(f)
  res = rbind(res, tmp)
  
}
```


### 3
```{r}
show_mean = function(df){
  for (i in colnames(df)) {
    if(df[,i] %>% is.numeric()){
      print(paste(
        i,
        mean(df[,i], na.rm = T),
        sep = ": "))
    }
    
  }
}


show_mean(iris)
```


### 4
```{r}
map_dbl(mtcars, mean)


map(mpg, unique) %>% map_int(., length)

map_dfc(ls, function(x){
  
  rpois(10, x)
  
})


# map_dfr(files,  read.csv)
```


### 5

#### 1
```{r}
five_squares <- (1:5)^2

map(list(five_squares),rnorm)
```
list(five_squares) is a  list of length one, in it there vector of length five, function works as that for each element in `list(five_squares)` do rnorm, the arguments for rnorm is default.



#### 2

```{r}
map(five_squares,rnorm)
```

the function works as: for each element in five squares, do rnorm, and the value of that element is for the first argument of rnorm.



```{r}
map(five_squares, rnorm, n = 5)
```

n replace the element of five squares as the the  first argument
for rnorm.




